### 2019-08-18 introduction.tex
TraMoS chapter ready.

The increasing number of discovered exoplanets have been reached thank to two techniques: Radial Velocity and Transits. Each one of these techniques had their own advantages depending on the physical properties of the planetary system. When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases proportionally to the size of the planet. Thus, its radius, in comparison with the radius of the star, can be determined directly using the Transit method. In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center. Therefore, the star will move in its own small orbit with a size proportional to the mass of the planet. In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$). The perfect scenario comes when both methods can be used in the same planetary system, allowing to derive essential properties such as the real mass and the mean density of the planet.

\begin{figure}[H]
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. This plot only shows the exoplanets with known masses}
\label{exoplanets}
\end{figure}

@@

This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter \ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo. I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.  I analized 22 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.

This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques and achievements to date. Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations. Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab, including  their observations and data reduction, light curve and RV analysis, measurements of TTVs and upper mass limit for possible companions in their systems. Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated. Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS and also, preliminary results of WASP-36b are shown. Finally, Chapter \ref{chap:conclusion} contains the principal conclusions of this thesis as well as some ideas for future work.

>>>>

The increasing number of discovered exoplanets have been reached thanks to two techniques: Radial Velocity and Transits (see Figure \ref{exoplanets}). Each one of these techniques had their own advantages depending on the physical properties of the planetary system. When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases proportionally to the size of the planet. Thus, its radius can be determined directly using the Transit method. In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center. Therefore, the star will move in its own small orbit with a size proportional to the mass of the planet. In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$). The perfect scenario comes when both methods can be used in the same planetary system, allowing to derive essential properties such as the real mass and the mean density of the planet.

The study of exoplanets does not end with their discovery.

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. This plot only shows the exoplanets with known masses}
\label{exoplanets}
\end{figure}

@@

This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter \ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo. I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.  I analized 27 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.

This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques and achievements to date. Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations. Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab, including  their observations and data reduction, light curve and RV analysis, measurements of TTVs and upper mass limit for possible companions in their systems. Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated. Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS. Finally, Chapter \ref{chap:conclusion} contains the principal conclusions of this thesis as well as some ideas for future work. The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.

### 2019-08-18 tramos.tex
TraMoS chapter ready.

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/tramos.png}
\caption{Histogram of the 30 transiting exoplanets with the largest amount of observations within the TraMoS project. The exoplanets WASP-4b and WASP5-b were presented in \cite{Hoyer2012} and \cite{Hoyer2013}. The results from the analysis of WASP-18b, WASP-19b and WASP77-Ab are in Cortés-Zuleta et al. 2019 (submitted, see Chapter \ref{chap:paper} for further details). In any of those systems a significant TTV signal was detected.}
\label{tramos}
\end{figure}

@@

\section{Transiting Exoplanets}
The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}). The Kepler mission was launched in 2009 and during its almost nine years of operation provided thousands of discoveries due to this method.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
\caption{Accumulative number of discovered exoplanets by year.}
\label{amount_exoplanet}
\end{figure}

@@

In Figure~\ref{transit} is described the architecture of a transiting exoplanet. Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).  When the planet passes in front of its star produced a dimming in its flux called primary transit. The maximum drop during the transit event defines the transit depth $\Delta{F}$:

@@

\section{Transit Timing Variations}

Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems? The idea of multiplanetary systems is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets. Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight. Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system, but this number is theoretically larger (cite).

@@

For a given light curve of a transiting exoplanet (see Fig. \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:

@@

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{imagenes/rms_ttv_amplitude}
\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit, around a star with $0.367~M_{\odot}$. The perturber is an Earth-mass planet. Panel \textbf{a} is an O-C diagram showing the measured TTV when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet. Panel \textbf{b} shows the TTV when the transiting planet and the perturbing planet are near an interior 2:1 resonance. The amplification of the TTV signal is by an order of magnitude. (Figure from \cite{Haghighipour2011})}
\label{rms_ttv_amplitude}
\end{figure}

@@

To date, only two hot Jupiters have been found to show TTV signals due to the presence of additional companions on their systems: WASP-47b \citep{Becker2015} and Kepler-730b \citep{Canas2019}, even though the TTV was proposed as a technique to search for additional companions of gas giants. The lack of observed companions in hot Jupiter systems could provide crucial information about planetary formation processes.

Through the TTV method not only the transiting exoplanet is being studied but the whole planetary system. Even the lack of variation in the transit timing gives clues related to the formation of close-in gas giant.

The no detection of TTV is also important: architecture of the system.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\columnwidth]{imagenes/tramos.png}
\caption{Histogram of the 30 transiting exoplanets with the largest amount of observations within the TraMoS project. The exoplanets WASP-4b and WASP5-b were presented in \cite{Hoyer2012} and \cite{Hoyer2013}. The results from the analysis of WASP-18b, WASP-19b and WASP77-Ab are in Cortés-Zuleta et al. 2019 (submitted, see Chapter \ref{chap:paper} for further details). In none of those systems a significant TTV signal was detected.}
\label{tramos}
\end{figure}

@@

In the following section \ref{lightcurve}, I describe the light curve produced from a transiting exoplanet --the principal target of the TraMoS project --  what information about the planet can be obtain from them and how these light curves can give us information about the architecture of this kind of systems. Then, in section \ref{ttv}, I detail on an specific type of phenomena of transiting exoplanets: the variation of the transit time of its light curve (TTV).

\section{Transiting exoplanets' light curve\label{lightcurve}}
The Transit method is today the most successful technique to discover extrasolar planets (see Figure \ref{amount_exoplanet}). The Kepler mission was launched in 2009 and during its almost nine years of operation provided thousands of discoveries due to this method.

\begin{figure}[ht]
\centering
\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
\caption{Accumulative number of discovered exoplanets by year and their corresponding method of discovery. To date, the Transit technique, along with Radial Velocity, are the most successful methods to discovery exoplanets. Figure from the NASA Exoplanet Archive (\url{exoplanetarchive.ipac.caltech.edu})}
\label{amount_exoplanet}
\end{figure}

@@

In Figure~\ref{transit} is described the architecture of a transiting exoplanet. Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations \cite{Seager2003,Winn2010}.  When the planet passes in front of its star produced a dimming in its flux called primary transit. The maximum drop during the transit event defines the transit depth $\Delta{F}$:

@@

\section{Transit Timing Variations\label{ttv}}

Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems? The idea of multiplanetary systems is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets. Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight. Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system\footnote{Information obtained from the NASA Exoplanet Archive \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger. \cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation in Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days-orbit.

@@

For a given light curve of a transiting exoplanet (see Figure \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/jupiter_ttv.pdf}
\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit and an Earth-mass perturber planet. The top panel is an Observed minus Computed diagram showing the measured TTV of the Jupiter-mass planet when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet. The panel at the bottom shows the TTV of the transiting planet when both are near an interior 2:1 resonance. In this case the small planet has a period of 19.7 days. The amplification of the TTV signal is by an order of magnitude. Figure generated with the Python package: \texttt{ttv2fast2furious}.}
\label{rms_ttv_amplitude}
\end{figure}

@@

To date, only two hot Jupiters have been found to show TTV signals due to the presence of additional companions on their systems: WASP-47b \citep{Becker2015} and Kepler-730b \citep{Canas2019}, even though the TTVs was proposed as a technique to search for additional companions of gas giants. The lack of observed companions in hot Jupiter systems could provide crucial information about planetary formation processes. Through the TTV method not only the transiting exoplanet is being studied but the whole planetary system.

\cite{Steffen2012b} analyzed Kepler data in order to constraint the occurrence rate of companions in hot Jupiter system. In a sample of 63 hot Jupiter candidates, none of them show evidence of possible companions in their system. When comparing with other types of exoplanets, 30\% of hot Neptunes candidates could have companions and 10\% of warm Jupiter candidates. This could suggest that hot Jupiter may have a different formation processes on which smaller companions are not allowed in their system: probably they are ejected through planet-planet scatter during migration. TTV studies could provide important clues about formation processes and dynamical evolution, and their mass and period dependence.
